### 2020-08-05 data/draft-publications.tex
postdocs code, data; first generation

\begin{enumerate}
\item 2. S. Aiyappan, A. K. Nandakumaran and Ravi Prakash, Semi-linear optimal control problem on a smooth oscillating domain Communications in Contemporary Mathematics, {\em Communications in Contemporary Mathematics} {\bf } (2019), 26 pages.
\item 1. S. Aiyappan, A. K. Nandakumaran and Abu Sufian, Asymptotic Analysis of a Boundary Optimal Control Problem on a General Branched Structure, to appear in Mathematical Methods in Applied Sciences (MMAS).
\item Benedetti, Carolina and González D’León, Rafael S. and Hanusa, Christopher R.H. and Harris, Pamela E. and Khare, Apoorva and Morales, Alejandro H. and Yip, Martha, A combinatorial model for computing volumes of flow polytopes, {\em Transactions of the American Mathematical Society} {\bf 372} (2019), 3369-3404.
\item Subhajit Ghosh, Total variation cutoff for the transpose top-2 with random shuffle, to appear in Journal of Theoretical Probability.
\item G. K. Basak, M. K. Ghosh and D. Mukherjee, A Stochastic Model with Inflation, Growth and Technology for the Political Business Cycle, {\em Journal of Computational Economics} {\bf 53} (2019), 125-140.
\item Arvind Ayyer and Pooja Singla, Random motion on finite rings, I: commutative rings, {\em Algebras and Representation theory} {\bf } (), .
\item E.K.Narayanan and Pooja Singla, On monomial representations of finitely generated nilpotent groups, {\em Communications in Algebra} {\bf 46} (2018), 2319–2331.
\item Souvik Dhara, Remco van der Hofstad, Johan S.H. van Leeuwaarden, Sanchayan Sen, Heavy-tailed configuration models at criticality, to appear in Annales de l'Institut Henri Poincaré (B) Probabilités et Statistiques.
\item Siddhartha Gadgil, Homogeneous Length Functions on Groups: Intertwined Computer and Human Proofs, to appear in Journal of Automated Reasoning.
\item Srikanth K. Iyer, The Random Connection Model - Connectivity, Edge Lengths and Degree Distributions, {\em Random Structures and Algorithms} {\bf 52} (2018), 283-300.
\item Rahul Vaze, Srikanth K. Iyer, Capacity of Cellular Wireless Networks, {\em IEEE Transactions on Wireless Communications} {\bf 18} (2019), 1490 - 1503.
\item Gokul Nair, Senthil Athmanathan,, Srikanth K. Iyer  and Vishwesha Guttal, Fission-fusion dynamics and group-size-dependent composition in heterogeneous populations, {\em Physical Review E} {\bf 99} (2019), .
\item Subhojoy Gupta, Meromorphic quadratic differentials and measured foliations on a Riemann surface, {\em Mathematische Annalen} {\bf 373} (2019), 73-118.
\item Subhojoy Gupta and Harish Seshadri, On domains biholomorphic to Teichmüller spaces, to appear in International Mathematics Research Notices.
\item Subhojoy Gupta, Harmonic maps and wild Teichmüller spaces, to appear in ournal of Topology and Analysis.
\item Subhojoy Gupta, Limits of harmonic maps and crowned hyperbolic surfaces, to appear in Transactions of the AMS.
\item Luz Roncal and Sundaram Thangavelu, An extension problem and trace Hardy inequality for the sublaplacian on H-type groups, to appear in IMRN.
\item Pradeep Boggarapu, Luz Roncal and Sundaram Thangavelu, On extension problem, trace Hardy and Hardy's inequalities for some fractional Laplacians, to appear in Communications in Pure and Applied Analysis..
\item Indranil Biswas and Vamsi Pritham Pingali, Metric properties of parabolic ample bundles, to appear in International Mathematical Research Notices.
\item Vamsi Pingali and Dror Varolin, Non-uniformly flat affine algebraic hypersurfaces, to appear in Nagoya mathematical journal.
\end{enumerate}

@@

\begin{enumerate}
\item Kriti Goel, Dilip Patil and Jugal Verma, Nullstellens\"atze and Applications {\em } ().
\item Dilip P Patil and Jugal Verma, Rational points and generalized trace forms on a finite algebra over a real closed field {\em } ().
\end{enumerate}

@@

\begin{enumerate}
\item Belton, Alexander and Guillot, Dominique and Khare, Apoorva and Putinar, Mihai, A panorama of positivity: I. Dimension free in {\em Birkhauser, Trends in Mathematics}{f } (2019), 117-165.
\item Belton, Alexander and Guillot, Dominique and Khare, Apoorva and Putinar, Mihai, A panorama of positivity: II. Fixed dimension in {\em American Mathematical Society, Contemporary Mathematics}{f } (), .
\item Subhojoy Gupta and Harish Seshadri , Complex geometry of Teichmüller domains in {\em EMS, Handbook of Teichmüller theory}{f 7} (), .
\item Subhojoy Gupta, Holomorphic quadratic differentials in Teichmüller theory in {\em EMS, Handbook of Teichmüller Theory}{f 7} (), .
\end{enumerate}

@@

\begin{enumerate}
\item Apoorva Khare, Smooth entrywise positivity preservers, a Horn–Loewner master theorem, and Schur polynomial identities, preprint.
\item Apoorva Khare, The non-compact normed space of norms on a finite-dimensional Banach space, preprint.
\item Projesh Nath Choudhury and Apoorva Khare, Distance matrices of a tree: two more invariants, and in a unified framework, preprint.
\item Arvind Ayyer, Matthieu Josuat-Vergès, Sanjay Ramassamy, Extensions of partial cyclic orders and consecutive coordinate polytopes , preprint.
\item Arvind Ayyer, Pooja Singla, Random motion on finite rings, II: Noncommutative rings , preprint.
\item Arvind Ayyer, Amritanshu Prasad, Steven Spallone, Macdonald trees and determinants of representations for finite Coxeter groups , preprint.
\item Dilip P. Patil, On the connectedness of the fiber product of two connected finte free affine schemes. , preprint.
\item Gautam Bharali and Anwoy Maitra, A weak notion of visibility, a family of examples, and Wolff--Denjoy theorems, submitted for publication.
\item Arvind Ayyer and Pooja Singla, Random motion on finite rings, II: Noncommutative rings, preprint.
\item M. Hassain and Pooja Singla, Representation Growth of Special Compact Linear Groups of Order Two, preprint.
\item Shiv Prakash Patel and Pooja Singla, A multiplicity one theorem for groups of type $A_n$ over discrete valuation rings, preprint.
\item Shifra Reif, R. Venkatesh, On tensor products of irreducible integrable representations, preprint.
\item Deniz Kus, R. Venkatesh, Borel-de Siebenthal theory for affine reflection systems, preprint.
\item Louigi Addario-Berry, Sanchayan Sen, Geometry of the minimal spanning tree of a random 3-regular graph, preprint.
\item Sourav Hait, Sayan Bagchi, Luz Roncal and Sundaram Thangavelu, On the lacunary spherical maximal function on the Heisenberg group, preprint.
\item TIRTHANKAR BHATTACHARYYA, SUBRATA SHYAM ROY, AND TAPESH YADAV, THE AGLER-YOUNG CLASS, submitted for publication.
\item Tirthankar Bhattacharyya, B. Krishna Das, Haripada Sau, Toeplitz operators and pseudo-extensions, submitted for publication.
\item Tirthankar Bhattacharyya, Anindya Biswas, Vikramjeet Singh Chandel, On the Nevanlinna problem - Characterization of all Schur-Agler class solutions affiliated with a given kernel, submitted for publication.
\item Tirthankar Bhattacharyya, B. Krishna Das, Haripada Sau, Toeplitz operators on the symmetrized bidisc, submitted for publication.
\item Vamsi Pritham Pingali, A vector bundle version of the Monge-Ampere equation, preprint.
\item Ved V. Datar and Vamsi Pritham Pingali, On coupled constant scalar curvature Kaehler metrics, preprint.
\item Ved Datar, Adam Jacob, Yuguang Zhang, Adiabatic limits of anti-self-dual connections on collapsed K3 surfaces, preprint.
\item Ved V. Datar, Vamsi Pritham Pingali, On coupled constant scalar curvature K\"ahler metrics, preprint.
\end{enumerate}

@@

\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi, Generalization of unfolding operator for highly oscillating
smooth boundary domains and homogenization {\em Calc. Var. Partial Differential Equations} {\bf 57} (2018), Art. 86, 30.
\item Akutagawa, Kazuo and Endo, Hisaaki and Seshadri, Harish, A gap theorem for positive {E}instein metrics on the
four-sphere {\em Math. Ann.} {\bf 373} (2019), 1329--1339.
\item Amritkar, R. E. and Rangarajan, G., Spatially synchronous extinction of species under external forcing {\em Physical Review Letters} {\bf 96} (2006), 258102.
\item Anamby, Pramath and Das, Soumya, Distinguishing {H}ermitian cusp forms of degree 2 by a certain
subset of all {F}ourier coefficients {\em Publ. Mat.} {\bf 63} (2019), 307--341.
\item Anamby, Pramath and Das, Soumya, Bounds for the {P}etersson norms of the pullbacks of
{S}aito-{K}urokawa lifts {\em J. Number Theory} {\bf 191} (2018), 289--304.
\item Arunkumar, G. and Kus, Deniz and Venkatesh, R., Root multiplicities for {B}orcherds algebras and graph
coloring {\em J. Algebra} {\bf 499} (2018), 538--569.
\item Ayyer, A. and Finn, C. and Roy, D., Matrix product solution of a left-permeable two-species asymmetric exclusion process {\em Physical Review E} {\bf 97} (2018), 5225.
\item Ayyer, Arvind and Behrend, Roger E., Factorization theorems for classical group characters, with

@@

partitions {\em J. Combin. Theory Ser. A} {\bf 165} (2019), 78--105.

@@

Linusson, Svante and Nunzi, Fran\c{c}ois, Bumping sequences and multispecies juggling {\em Adv. in Appl. Math.} {\bf 98} (2018), 100--126.
\item Ayyer, Arvind and Finn, Caley and Roy, Dipankar, Matrix product solution of a left-permeable two-species
asymmetric exclusion process {\em Phys. Rev. E} {\bf 97} (2018), 012151, 10.
\item Ayyer, Arvind and Finn, Caley and Roy, Dipankar, The phase diagram for a multispecies left-permeable asymmetric
exclusion process {\em J. Stat. Phys.} {\bf 174} (2019), 605--621.
\item Ayyer, Arvind and Prasad, Amritanshu and Spallone, Steven, Odd partitions in {Y}oung's lattice {\em S\'{e}m. Lothar. Combin.} {\bf 75} (2018), Art. B75g, 13.
\item Ayyer, Arvind and Ramassamy, Sanjay, The {H}ilbert-{G}alton board {\em ALEA Lat. Am. J. Probab. Math. Stat.} {\bf 15} (2018), 755--774.
\item B\"{o}cherer, Siegfried and Das, Soumya, Cuspidality and the growth of {F}ourier coefficients of
modular forms {\em J. Reine Angew. Math.} {\bf 741} (2018), 161--178.
\item B\"{o}cherer, Siegfried and Das, Soumya, Petersson norms of not necessarily cuspidal {J}acobi modular
forms and applications {\em Adv. Math.} {\bf 336} (2018), 335--376.
\item Bagchi, Sayan and Thangavelu, Sundaram, Weighted norm inequalities for {W}eyl multipliers and fourier
multipliers on the {H}eisenberg group {\em J. Anal. Math.} {\bf 136} (2018), 1--29.
\item Baklouti, Ali and Thangavelu, Sundaram, Hardy and {M}iyachi theorems for {H}eisenberg motion groups {\em Nagoya Math. J.} {\bf 229} (2018), 1--20.
\item Balhara, Rakesh, Hardy's inequality for the fractional powers of the {G}rushin
operator {\em Proc. Indian Acad. Sci. Math. Sci.} {\bf 129} (2019), Art. 33, 25.
\item Balodi, Mamta and Palcoux, Sebastien, On {B}oolean intervals of finite groups {\em J. Combin. Theory Ser. A} {\bf 157} (2018), 49--69.
\item Banerjee, Abhishek, On {A}uslander's formula and cohereditary torsion pairs {\em Commun. Contemp. Math.} {\bf 20} (2018), 1750071, 27.
\item Banerjee, Abhishek, Modular {H}ecke algebras over {M}\"{o}bius categories {\em J. Geom. Phys.} {\bf 131} (2018), 23--40.
\item Banerjee, Abhishek, A topological {N}ullstellensatz for tensor-triangulated
categories {\em C. R. Math. Acad. Sci. Paris} {\bf 356} (2018), 365--375.
\item Banerjee, Abhishek, Quasimodular {H}ecke algebras and {H}opf actions {\em J. Noncommut. Geom.} {\bf 12} (2018), 1041--1080.
\item Banerjee, Abhishek, Completions of monoid objects and descent results {\em J. Algebra} {\bf 507} (2018), 362--399.
\item Basu, Arnab and Ghosh, Mrinal K., Nonzero-sum risk-sensitive stochastic games on a countable

>>>>

\item S Aiyappan, A. K. Nandakumaran and Abu Sufian, \emph{Asymptotic analysis of Boundary Optimal Control Problem on a General Branched Structure},  Mathematical Methods in the Applied Sciences {\bf 42} (2019. DOI: 10.1002/mma.5748), 6407-6434 , DOI 10.1002/mma.5748.
\item K. Murali, A. K. Nandakumaran, Turgurt Durduran, Hari M Varma, \emph{Recovery of the diffuse correlation spectroscopy data-type from speckle contrast measurements: towards low-cost, deep-tissue blood flow measurements}, Biomedical Optics Express 5395 {\bf 10} (2019), .
\item S Aiyappan, A. K. Nandakumaran and Ravi Prakash, \emph{Locally Periodic Unfolding Operator for Highly Oscillating Rough Domains}, Annali di Matematica Pura ed Applicata {\bf 198} (2019), 1931-1954, DOI 10.1007/s10231-019-00848-7.
\item S Aiyappan, A. K. Nandakumaran and Ravi Prakash, \emph{Semi-linear optimal control problem on a smooth oscillating domain}, Communications in Contemporary Mathematics {\bf } (2019), 1-26, DOI 10.1142/S0219199719500299.
\item S Aiyappan, Editha C. Jose, Ivy Carol B. Lomerio and A. K. Nandakumaran, \emph{ Control Problem on a Rough Circular Domain and Homogenization}, Asymptotic Analysis {\bf 115} (2019),  19-46, DOI 10.3233/ASY-191526.
\item Khare, Apoorva and Rajaratnam, Bala, \emph{Probability inequalities and tail estimates for metric semigroups}, Advances in Operator Theory (Special issue in honor of Rajendra Bhatia) {\bf 5} (2020), 779-795, DOI 10.1007/s43036-020-00048-8, \url{https://link.springer.com/article/10.1007%2Fs43036-020-00048-8}.
\item Ghosh, Subhajit, \emph{Total Variation Cutoff for the Transpose Top-2 with Random Shuffle}, to appear in Journal of Theoretical Probability, DOI 10.1007/s10959-019-00945-6, \url{https://link.springer.com/article/10.1007%2Fs10959-019-00945-6}.
\item Datta, B. and Gupta, S., \emph{Semi-regular tilings of the hyperbolic plane \label{bdsg_2019} }, to appear in Discrete Comput Geom, DOI https://doi.org/10.1007/s00454-019-00156-0, \url{https://doi.org/10.1007/s00454-019-00156-0}.
\item Datta, B. and Sarkar, S., \emph{Equilibrium triangulations of some quasitoric 4-manifolds}, Southeast Asian Bull. Math. {\bf 44} (2020), 57--78.
\item Datta, B. and Maity, D., \emph{Correction to: Semi-equivelar and vertex-transitive maps on the torus}, Beitr Algebra Geom {\bf 61} (2020), 187--188.
\item Martin Kreuzer and Dilip P. Patil , \emph{COMPUTATIONAL ASPECTS OF BURNSIDE RINGS PART II: IMPORTANT MAPS}, to appear in Beiträge zur Algebra und Geometrie / Contributions to Algebra and Geometry.
\item Bharali, Gautam and Maitra, Anwoy, \emph{A weak notion of visibility, a family of examples, and Wolff--Denjoy theorems}, to appear in Annali della Scuola Normale Superiore di Pisa, DOI 10.2422/2036-2145.201906_007, \url{http://annaliscienze.sns.it/index.php?page=ForthcomingArticles}.
\item Maitra, Anwoy, \emph{On the continuous extension of Kobayashi isometries}, Proc. Amer. Math. Soc. {\bf 148} (2020), 3437--3451, \url{https://www.ams.org/journals/proc/2020-148-08/S0002-9939-2020-15038-1/}.
\item Vishnu Priya, N. and Senthilvelan, M. and  Rangarajan, G. and Lakshmanan, M, \emph{On symmetry preserving and symmetry broken bright, dark and antidark soliton solutions of nonlocal nonlinear Schrödinger equation}, Physics Letters A {\bf 383} (2019), 15-26.
\item Kashyap, G. A. R. S. R. K. and Bapat, D. and Das, D. and Gowaikar, R. D. and Amritkar, R. E. and Rangarajan, G. and Ravindranath, V. and Ambika, G, \emph{Synapse loss and progress of Alzheimer’s disease - A network model}, Scientific Reports {\bf 9} (2019), 6555.
\item Vishnu Priya, N. and Senthilvelan, M. and Rangarajan, G., \emph{On the role of four-wave mixing effect in the interactions between nonlinear modes of coupled generalized nonlinear Schrodinger equation}, Chaos {\bf 29} (2019), 123135.
\item Sarkar, Amar Deep and Verma, Kaushal, \emph{A submultiplicative property of the Carath\'{e}odory metric on planar domains}, Proc. Indian Acad. Sci. (Math. Sci.) {\bf } (), , \url{https://www.ias.ac.in/article/fulltext/pmsc/130/0035}.
\item Frauke Bleher, Ted Chinburg, Ralph Greenberg, Mahesh Kakde, George Pappas, Romyar Sharifi, Martin Taylor, \emph{Higher Chern Classes in Iwasawa Theory}, American Journal of Mathematics {\bf 142} (2020), 627-682, \url{https://muse.jhu.edu/issue/42062}.
\item Basu, R. and Ganguly, S. and Hegde, M. and Krishnapur, M., \emph{Lower Deviations in β-ensembles and Law of Iterated Logarithm in Last Passage Percolation}, to appear in Israel Journal of Mathematics.
\item M. K. Ghosh and S. Pradhan, \emph{Zero-Sum Risk-Sensitive Stochastic Differential Games with Reflecting Diffusions in the Orthant}, to appear in ESIAM: Control, Optimization and Calculus of Variations , DOI Doi:10.105/cocv/2020029.
\item M. K. Ghosh, K. Suresh Kumar, C. Pal and S. Pradhan, \emph{Nonzero-sum risk-sensitive stochastic differential games with discounted costs, Stochastic Analysis and Applications}, to appear in Stochastic Analysis and Applications, DOI Doi: 10.1080/07362994.2020.1796707.
\item Iyer, S. K. and Yogeshwaran, D., \emph{Thresholds for vanishing of isolated faces in random Cech and Vietoris-Rips Complexes}, Annals de l'Institut Henri Poincar$\acute{e}$ - Probabiliti$\acute{e}$s et Statistiques {\bf 56} (2020), 1869-1897, \url{https://doi.org/10.1214/19-AIHP1020}.
\item Datta, Basudeb and Gupta, Subhojoy, \emph{Semi-regular tilings of the hyperbolic plane}, to appear in Discrete and Computational Geometry, DOI https://doi.org/10.1007/s00454-019-00156-0.
\item Thirupathi Gudi, Ramesh Ch. Sau, \emph{Finite Element Analysis of the Constrained Dirichlet Boundary Control Problem Governed by the Diffusion Problem}, to appear in ESAIM: Control, Optim. Calc. Var, DOI doi: 10.1051/cocv/2019068..
\item Bhattacharyya, Tirthankar and Biswas, Anindya and Chandel, Vikramjeet Singh, \emph{On the Nevanlinna problem: characterization of all Schur–Agler class solutions affiliated with a given kernel},  Studia Math. {\bf 255} (2020), 83–107., DOI 10.4064/sm190505-8-10.
\item Bhattacharyya, Tirthankar and Das, Bata Krishna and Sau, Haripada, \emph{Toeplitz operators on the symmetrized bidisc}, International Mathematics Research Notices (IMRN) {\bf } (), , DOI 10.1093/imrn/rnz333.
\item Pingali, Vamsi Pritham and Varolin, Dror, \emph{Nonuniformly flat affine algebraic hypersurfaces}, to appear in Nagoya Mathematical Journal, DOI https://doi.org/10.1017/nmj.2019.2, \url{https://www.cambridge.org/core/journals/nagoya-mathematical-journal/article/nonuniformly-flat-affine-algebraic-hypersurfaces/3704C1133CB22A05D7FB13765156FC4E}.
\item Alvarez-Consul, Luis and Garcia-Fernandez, Mario  and García-Prada, Oscar and Pingali, Vamsi Pritham , \emph{Gravitating vortices and the Einstein–Bogomol’nyi equations}, to appear in Mathematische Annalen, DOI https://doi.org/10.1007/s00208-020-01964-z, \url{https://link.springer.com/content/pdf/10.1007/s00208-020-01964-z.pdf}.
\item Datar, Ved and Jacob,Adam and Zhang, Yuguang, \emph{Adiabatic limits of anti-self-dual connections on collapsed K3 surfaces}, to appear in Journal of differential geometry, \url{https://arxiv.org/pdf/1809.08583.pdf}.
\item Datar, Ved and Pingali, Vamsi Pritham, \emph{On coupled constant scalar curvature Kaehler metrics}, to appear in Journal of symplectic geometry, \url{https://arxiv.org/pdf/1901.10454v2.pdf}.
\item Pradhan, P. and Sahu, B., \emph{A characterization of the family of secant lines to a hyperbolic quadric in PG(3,q), q odd}, Discrete Mathematics {\bf 343} (2020), , DOI 10.1016/j.disc.2020.112044, \url{https://doi.org/10.1016/j.disc.2020.112044}.
\item Arun Maiti, \emph{Quasi-vertex-transitive maps on the plane}, Discrete Mathematics {\bf 343} (2020), 111911-111917, \url{https://www.sciencedirect.com/science/article/pii/S0012365X20301035}.
\item Datt, Gopal and Kumar, Sanjay, \emph{A criterion for quasinormality in $\mathbb{C}^n$},  Proc. Indian Acad. Sci. Math. Sci. {\bf 129} (2019), Paper No. 11, 13 pp., DOI https://doi.org/10.1007/s12044-018-0449-5     (This article was published before the review period i.e., April 1, 2019, BUT this is not yet included on the page  https://siddhartha-gadgil.github.io/DeptWeb/pubs.html), \url{https://link.springer.com/article/10.1007/s12044-018-0449-5?shared-article-renderer}.
\item Hatui, Sumana, \emph{Schur multipliers of special p-groups of rank 2}, Journal of Group Theory {\bf 23} (2020), 85-95, DOI https://doi.org/10.1515/jgth-2019-0045, \url{https://www.degruyter.com/view/journals/jgth/23/1/article-p85.xml}.
\item Choudhury, Projesh Nath and Tsatsomeros Michael J., \emph{Algorithmic Detection and Construction of N-matrices}, Linear Algebra and Its Applications {\bf 602} (2020), 46-56, DOI 10.1016/j.laa.2020.04.028, \url{https://doi.org/10.1016/j.laa.2020.04.028}.
\item Choudhury, Projesh Nath and Sivakumar, K.C., \emph{Matrices with Positive Semidefinite Real Part}, to appear in Linear and Multilinear Algebra, DOI 10.1080/03081087.2019.1602588, \url{https://doi.org/10.1080/03081087.2019.1602588}.
\item Chim, Kwok Chi; Shorey, Tarlok Nath; Sinha, Sneh Bala , \emph{On Baker's explicit abc-conjecture},  Publ. Math. Debrecen {\bf 94} (2019), 435–453.
\item Carstensen, C. and Mallik, G. and Nataraj, N., \emph{Nonconforming Finite Element Discretization for Semilinear Problems with Trilinear Nonlinearity}, IMA Journal of Numerical Analysis {\bf } (2020), , DOI https://doi.org/10.1093/imanum/drz071, \url{https://doi.org/10.1093/imanum/drz071}.
\item Mal, Arpita and Sain, Debmalya and Paul, Kallol, \emph{On some geometric properties of operator spaces}, Banach J. Math. Anal. {\bf 13} (2019), 174-191, \url{https://projecteuclid.org/euclid.bjma/1543914019}.

@@

@@

@@

\item Khare, Apoorva, \emph{Sharp nonzero lower bounds for the Schur product theorem}, submitted for publication, \url{https://arxiv.org/abs/1910.03537}.
\item Lübeck, Frank and Prasad, Dipendra and Ayyer, Arvind, \emph{A character relationship between symmetric group and hyperoctahedral group }, preprint, \url{https://arxiv.org/abs/1912.08576}.
\item Ayyer, Arvind and Sinha, Shubham , \emph{The size of t-cores and hook lengths of random cells in random partitions }, preprint, \url{https://arxiv.org/abs/1911.03135}.
\item Ayyer, Arvind, \emph{ A simple symmetric exclusion process driven by an asymmetric tracer particle }, preprint, \url{https://arxiv.org/abs/2001.02425}.
\item David Burns, Mahesh Kakde, \emph{On Weil-Etale Cohomology and Artin L-series}, preprint, \url{https://nms.kcl.ac.uk/david.burns/web_page/bk.pdf}.
\item Gupta, Purvi and Wawrzyniak, Chloe Urbanski, \emph{STABILITY OF THE HULL(S) OF AN $n$-SPHERE IN $\mathbb{C}^n$}, submitted for publication, \url{https://arxiv.org/pdf/2002.08699.pdf}.
\item Radhika Ganapathy, \emph{A Hecke algebra isomorphism over close local fields}, preprint.
\item Miermont, Grégory and Sen, Sanchayan , \emph{On breadth-first constructions of scaling limits of random graphs and random unicellular maps}, submitted for publication, \url{https://arxiv.org/abs/1908.04403}.
\item Gupta, Subhojoy and Mj, Mahan, \emph{Meromorphic projective structures, grafting and the monodromy map}, preprint, \url{http://arxiv.org/abs/1904.03804}.
\item Gupta, Subhojoy, \emph{Monodromy groups of CP^1-structures on punctured surfaces}, preprint, \url{https://arxiv.org/abs/1909.10771}.
\item Biswas, Indranil and Gupta, Subhojoy and Mj, Mahan and Whang, Junho Peter, \emph{Surface group representations in SL(2,C) with finite mapping class orbits}, preprint, \url{https://arxiv.org/abs/1707.00071}.
\item Ganguly, Pritam and Thangavelu,Sundaram, \emph{On lacunary spherical maximal function on Heisenberg groups}, preprint.
\item Bhattacharyya, Tirthankar and Kumar, Poornendu and Sau, Haripada, \emph{Distinguished Varieties Through the Berger--Coburn--Lebow Theorem}, submitted for publication, \url{https://arxiv.org/pdf/2001.01410.pdf}.
\item Bhattacharyya, T. and  Biswas, A. and Maitra, A., \emph{An unbounded realization of the symmetrized bidisc}, submitted for publication, \url{https://arxiv.org/pdf/2005.00289.pdf }.
\item Pingali, Vamsi Pritham, \emph{The deformed Hermitian Yang-Mills equation on three-folds}, preprint, \url{https://arxiv.org/abs/1910.01870}.
\item Garcia-Fernandez, Mario and Pingali, Vamsi Pritham and Yao, Chengjian , \emph{Gravitating vortices with positive curvature}, preprint, \url{https://arxiv.org/abs/1911.09616}.
\item Quddus, Safdar, \emph{Equivariant Cartan Homotopy Formula for $DG$-algebra.}, preprint, \url{https://arxiv.org/abs/2002.02192}.
\item Arun Maiti, \emph{OPTIMAL INDEX GROWTH OF CLOSED GEODESICS}, submitted for publication.
\item  Poria, Anirudha, \emph{Uncertainty Principles for the Fourier and the Short-Time Fourier Transforms}, submitted for publication, \url{https://arxiv.org/abs/2004.04184}.
\item Poria, Anirudha, \emph{Uncertainty principles for the Opdam-Cherednik transform on modulation spaces}, submitted for publication, \url{https://arxiv.org/abs/2005.14274}.
\item Bera, Sudip, \emph{ENUMERATION OF WEIGHTED PATHS ON A DIGRAPH AND BLOCK HOOK DETERMINANT}, submitted for publication.
\item Behera, Kiran Kumar, \emph{Self-inversive polynomials from rational transformation of linear functionals}, submitted for publication, \url{https://arxiv.org/abs/1909.12548}.
\item Hatui, Sumana and Singla Pooja, \emph{On Schur multiplier and Projective representations of Heisenberg groups}, submitted for publication, \url{https://arxiv.org/abs/1909.06589}.
\item Chattopahyay, Arup and Sarkar, Jaydeb and Sarkar, Srijan, \emph{Multiplicities, invariant subspaces and an additive formula.}, preprint, \url{https://arxiv.org/abs/1812.05435}.
\item Ghara, Soumitra and Kumar, Surjit and Pramanick, Paramita, \emph{$K$-homogeneous tuple of operators on bounded symmetric domains}, preprint.

@@

\item Aas, Erik and Ayyer, Arvind and Linusson, Svante and Potka,
Samu, {\em The exact phase diagram for a semipermeable {TASEP} with
nonlocal boundary jumps}, J. Phys. A} {\bf 52} (2019), 355001, 19, DOI 10.1088/1751-8121/ab2e96, \url{https://doi.org/10.1088/1751-8121/ab2e96}.
\item Aiyappan, S. and Jose, Editha C. and Lomerio, Ivy Carol B. and
Nandakumaran, A. K., {\em Control problem on a rough circular domain and homogenization}, Asymptot. Anal.} {\bf 115} (2019), 19--46, DOI 10.3233/asy-191526, \url{https://doi.org/10.3233/asy-191526}.
\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi, {\em Locally periodic unfolding operator for highly oscillating
rough domains}, Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1931--1954, DOI 10.1007/s10231-019-00848-7, \url{https://doi.org/10.1007/s10231-019-00848-7}.
\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi, {\em Generalization of unfolding operator for highly oscillating
smooth boundary domains and homogenization}, Calc. Var. Partial Differential Equations} {\bf 57} (2018), Art. 86, 30, DOI 10.1007/s00526-018-1354-6, \url{https://doi.org/10.1007/s00526-018-1354-6}.
\item Aiyappan, S. and Nandakumaran, A. K. and Sufian, Abu, {\em Asymptotic analysis of a boundary optimal control problem on a
general branched structure}, Math. Methods Appl. Sci.} {\bf 42} (2019), 6407--6434, DOI 10.1002/mma.5748, \url{https://doi.org/10.1002/mma.5748}.
\item Aiyappan, S. and Sardar, Bidhan Chandra, {\em Biharmonic equation in a highly oscillating domain and
homogenization of an associated control problem}, Appl. Anal.} {\bf 98} (2019), 2783--2801, DOI 10.1080/00036811.2018.1471207, \url{https://doi.org/10.1080/00036811.2018.1471207}.
\item Akutagawa, Kazuo and Endo, Hisaaki and Seshadri, Harish, {\em A gap theorem for positive {E}instein metrics on the
four-sphere}, Math. Ann.} {\bf 373} (2019), 1329--1339, DOI 10.1007/s00208-018-1749-x, \url{https://doi.org/10.1007/s00208-018-1749-x}.
\item Anamby, Pramath and Das, Soumya, {\em Distinguishing {H}ermitian cusp forms of degree 2 by a certain
subset of all {F}ourier coefficients}, Publ. Mat.} {\bf 63} (2019), 307--341, DOI 10.5565/PUBLMAT6311911, \url{https://doi.org/10.5565/PUBLMAT6311911}.
\item Anamby, Pramath and Das, Soumya, {\em Bounds for the {P}etersson norms of the pullbacks of
{S}aito-{K}urokawa lifts}, J. Number Theory} {\bf 191} (2018), 289--304, DOI 10.1016/j.jnt.2018.03.011, \url{https://doi.org/10.1016/j.jnt.2018.03.011}.
\item Arunkumar, G. and Kus, Deniz and Venkatesh, R., {\em Root multiplicities for {B}orcherds algebras and graph
coloring}, J. Algebra} {\bf 499} (2018), 538--569, DOI 10.1016/j.jalgebra.2017.11.050, \url{https://doi.org/10.1016/j.jalgebra.2017.11.050}.
\item Ayyer, Arvind and Behrend, Roger E., {\em Factorization theorems for classical group characters, with

@@

partitions}, J. Combin. Theory Ser. A} {\bf 165} (2019), 78--105, DOI 10.1016/j.jcta.2019.01.001, \url{https://doi.org/10.1016/j.jcta.2019.01.001}.

@@

Linusson, Svante and Nunzi, Fran\c{c}ois, {\em Bumping sequences and multispecies juggling}, Adv. in Appl. Math.} {\bf 98} (2018), 100--126, DOI 10.1016/j.aam.2018.03.001, \url{https://doi.org/10.1016/j.aam.2018.03.001}.
\item Ayyer, Arvind and Finn, Caley and Roy, Dipankar, {\em Matrix product solution of a left-permeable two-species
asymmetric exclusion process}, Phys. Rev. E} {\bf 97} (2018), 012151, 10, DOI 10.1103/physreve.97.012151, \url{https://doi.org/10.1103/physreve.97.012151}.
\item Ayyer, Arvind and Finn, Caley and Roy, Dipankar, {\em The phase diagram for a multispecies left-permeable asymmetric
exclusion process}, J. Stat. Phys.} {\bf 174} (2019), 605--621, DOI 10.1007/s10955-018-2183-x, \url{https://doi.org/10.1007/s10955-018-2183-x}.
\item Ayyer, Arvind and Linusson, Svante, {\em Reverse juggling processes}, Random Structures Algorithms} {\bf 55} (2019), 56--72, DOI 10.1002/rsa.20825, \url{https://doi.org/10.1002/rsa.20825}.
\item Ayyer, Arvind and Prasad, Amritanshu and Spallone, Steven, {\em Odd partitions in {Y}oung's lattice}, S\'{e}m. Lothar. Combin.} {\bf 75} (2018), Art. B75g, 13.
\item Ayyer, Arvind and Ramassamy, Sanjay, {\em The {H}ilbert-{G}alton board}, ALEA Lat. Am. J. Probab. Math. Stat.} {\bf 15} (2018), 755--774, DOI 10.30757/alea.v15-28, \url{https://doi.org/10.30757/alea.v15-28}.
\item B\"{o}cherer, Siegfried and Das, Soumya, {\em Cuspidality and the growth of {F}ourier coefficients of
modular forms}, J. Reine Angew. Math.} {\bf 741} (2018), 161--178, DOI 10.1515/crelle-2015-0075, \url{https://doi.org/10.1515/crelle-2015-0075}.
\item B\"{o}cherer, Siegfried and Das, Soumya, {\em Petersson norms of not necessarily cuspidal {J}acobi modular
forms and applications}, Adv. Math.} {\bf 336} (2018), 335--376, DOI 10.1016/j.aim.2018.07.033, \url{https://doi.org/10.1016/j.aim.2018.07.033}.
\item Bagchi, Sayan and Thangavelu, Sundaram, {\em Weighted norm inequalities for {W}eyl multipliers and fourier
multipliers on the {H}eisenberg group}, J. Anal. Math.} {\bf 136} (2018), 1--29, DOI 10.1007/s11854-018-0053-8, \url{https://doi.org/10.1007/s11854-018-0053-8}.
\item Baklouti, Ali and Thangavelu, Sundaram, {\em Hardy and {M}iyachi theorems for {H}eisenberg motion groups}, Nagoya Math. J.} {\bf 229} (2018), 1--20, DOI 10.1017/nmj.2016.58, \url{https://doi.org/10.1017/nmj.2016.58}.
\item Balakumar, G. P. and Borah, Diganta and Mahajan, Prachi and
